---
title: "Vietnam FoF Survey Analysis - Journal"
author: "mz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
  number_sections: yes
toc: yes
toc_depth: 3
html_document: default
bibliography: "../misc/vn-lit.bib"
---
  
```{r "setup", include=FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require("knitr")
# opts_knit$set(root.dir = "/home/mz/Documents/Copy/Dropbox/analysis/Vietnam/VietnamSurvey")
opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
```


```{r "load data", include=FALSE}
# has to be in separate chunk from setup!
#load("data-old/working-copy.RData")
```

# Monday 23.10.2017 

Start checking new data.

Asked by GL to do a quick first trawl of the dataset. 

Move previous data into `data-old` folder start new journal - v.2


### Updated dir structure:

`*` indicate the folders and all their contents are hidden/non-public material. 
<!-- use tree /f /a > tree.txt to get output below -->
```
VietnamSurvey/
|   .gitignore
|   .Rhistory
|   VietnamSurvey.Rproj
|   
+---data/*
|   |   
|   \---data-raw/
|       +---DATA/
|       |   +---Excel/
|       |   |       Section_A-G.xls
|       |   |       Section_B.xls
|       |   |       Section_C.xls
|       |   |       Section_G3.xls
|       |   |       Section_H_K.xls
|       |   |       
|       |   \---Stata/
|       |           Section_A-G.dta
|       |           Section_B.dta
|       |           Section_C.dta
|       |           Section_G3.dta
|       |           Section_H_K.dta
|       |           
|       +---REPORT/
|       |       OIPA Farming Survey_IPPM Report_20170411.docx
|       |       
|       \---TOOLS/
|               OIPA_FoF Farming Quest_Eng_final_20161220.docx
|               OIPA_FoF Farming Quest_Vie_final_20161220.docx
|               
+---misc/
|       style.css
|       style.docx
|       vn-lit.bib
|       
+---old/*
|   +---data-old/*
|   |   |   full_data_v1_no_dup.dta
|   |   |   full_data_v1_no_dup_stata-12-11.dta
|   |   |   updated-copy.RData
|   |   |   working-copy.RData
|   |   |   
|   |   \---RawData/*
|   |           full_data_v1_no_dup.dta
|   |           OIPA_FoF Farming Quest_Eng_final_20161220.docx
|   |           OIPA_IPPM ToR for Survey in TB & VP Dec2016_final.pdf
|   |           
|   +---reports-old/*
|   |       r00-survey-variable-list-originals-only.pdf
|   |       r00-survey-variable-list.pdf
|   |       r01-data-analysis-journal-v01.pdf
|   |       r02-survey-issues.pdf
|   |       r03-first-cut.html
|   |       
|   \---scripts-old/*
|           00-my-functions.R 
|           00-scratchpad.R
|           01-data-import.R
|           02-new-variables.R
|           r00-survey-variable-list-originals-only.Rmd
|           r00-survey-variable-list.Rmd
|           r01-data-analysis-journal.pdf
|           r01-data-analysis-journal.Rmd
|           r02-survey-issues.docx
|           r02-survey-issues.Rmd
|           r03-first-cut.Rmd
|           
+---reports/*
\---scripts
        01-data-import.R
        r01-data-analysis-journal.Rmd
        style.docx
```


# Tuesday 24.10.2017 

* Clean up old stuff, now celar project
* Start import of data - `.dta` version
* Import Section_A-G.dta as `ds.1` 148 variables, 413 cases


# Thursday 26.10.2017 

* Import all 5 stata files, all 5 excel files and old stata file and compare number of cases


# Friday 27.10.2017 

* continue with checking three versions of data for missing cases. and write up.

After checks final import is based on:
* new stata files;
* removing hh member moved away 122-25 in section C 
* Saved into `tmp.clean.import.RData`
* `01-data-import.R` is finished = one off

Now start working on `02-data-clean.R`:

* merge into 3 tables
* add unique identifiers 
* this is where i Noticed Section B (hh menmbers) who are residents - there are actually 414 of them, so one too many...

# Monday 30.10.2017

* clean up plot table and add hh ids and unique identifiers. 
* 01-data-import is done
* 02-clean-data consolidates all files into 3 datasets in one RData file (`clean.RData`)


# Sunday 5.11.2017

* prepare variable list: `r00-survey-variable-list.Rmd`
* a few var (g19, g20) have unknown characters in descriptions, clean up in 02-data-clean
* do tables for all three datasets. 
* in ds.membr one var (mcode) has no description


Then the first trawl of the data: `r03-first-cut.Rmd`

* OK, table and plotting funcitons seem to be still working OK for nominal, just tweak for ds.hohh 
* If I add measurement type to the variable list, nominal and interval, i can maybe automate this more
* OK, semi automated now, but need to deal with missing values. tomorrow. 

# Monday 6.11.2017

Fix tables in first trawl

* Make sure missing values are labeled as such (in nominal tables)
* Make sure missing values in interval variables don't mess up the tables eiter (e.g. if one province has them and other doesnt)
* Make sure plots of interval variables also don't use missing 101s. 
* and then change the box plots to violin plots cause they're better

* whole section E is not coded properly. Labels need to be added/ 
* then there is the problem of missing horses and other vars with no valid answers.. 
* and the problem if one province has missing all values, but not the other 

More issues:

* Then note that there are some 'other' questions that have not been translated (g1119other, g1129other, g1139other)
* H12 and H13 should be main reason, but mulitple reasons are given 
* H15, H17 value 3 not labeled
* H1396, I1, I2, I3, K1, K31, K32, K33, K34, K396  wrong measurement, no labels.


Now have a look at the household member data as well. 

* Prepared household member first cut as well

# Tuesday 7.11.2017

Meeting with SH, GL and KH. Agree that I prepare the methods outline paper in two weeks. 
GL will have a look at the first cut and also try to get out of Long the methodology of the sampling.

# Wednesday 8.11.2017

Attempting clean up of project. 

In this process I note that there are duplicate labels in ds.hohh, which gets picked up by `as.data.frame` converting from  `memisc datasets, which I've never noticed before. Anyway, now I need to fix them manually: 

* Vars `d21`, `d22`, `d23` changed `2 = Agree` to `2 = Disagree`. This seems obviously to be a typo. Update `02-data-clean.R` with these. 

Funviton generalisation@

* FunNominal = table any combination of variables from any data set


# Monday 30.4.

Reboot.

# Tuesday 2.10.

Actually reboot here - these get a separate file, `r04-clarificaiton-questions.Rmd`, so look there for most up to date version. 

Questions for clarificaiton of the sampling procedure based on the Report. 

In the report you say: "The first condition was that households were active in farming activities in 2016 and then ranked them along with the size of farming."

1. Why did you rank them? 

2. Did you use the ranking in the sampling process - if so, how?

3. Was the selection of the households done by the communal admistrators? 

4. Was there a list of eligible households? How were they sampled?

In the report you go on to say: "The second condition to choose a representative for each selected household was that such a representative person was actively involved in farming work (doing the work directly) or decisively involved in investment for farming."

4. Was the sampling of households and choice of representative in each household done at the same time?

5. Was the respondent in each household decided in the field?

6. What if there were two respondents that fit this criteria, how did you decide between them?

In the report you say: "there were few people aged 30-50 to do farming, as they were doing some non-agricultural jobs (such as self-employed house constructors, and workers at foreign-invested factories)"

7. Does that mean that if someone was also some non-agricultural jobs, did you exclude them from the survey?

8. Does this mean that all respondents in the survey were doing only farming work?

9. Was this known before going into the field - did you know if heads of households were doing non-agricultural jobs before the interviews or did you find out during the interview and exclude them then?

10. Was there any difference in the sampling procedure of households between the two provinces?

11. Was there any difference in the sampling procedure of the respondents between the two provinces?

12. Did the following organisations help in the selection of households and respondents: The Vietnamese Association of the Elderly, the Farmer's Union, Vienam Women's Union? What was their role?

13. The average household size (including members that have migrated) is 3.1 in Thai Binh and 4.6 in Vinh Phuc. Is that what you would expect? If not, why the discrepancy?

14. The migration rates (household members not living in the household) are higher in Thai Bing (7 %) than in Vinh Phuc (10 %). Is that what you would expect?


# Wednesday 3.10.

Send off questions for Long to George - see version above. 

SH wants a first cut of all the questions for only women over 50. 

# Thursday 4.10.


1. Hm, there is an issue in vars 48-149. 

2. Let me first add var id- (i) to the variable list file, just jo make it easier to look for variables. (Also, there was an overlap in 149, but no big deal)

3. OK, the error in 1. is caused by there being no horses, so all the values are `*101`, i.e. missing. The `FunIntervalBoxplot()` function has to be fixed so it can accommodate that. 

4. So I've added a condition that the (province!) split has to have at least one vector that has lenght >0. Should work now, but lemme find an example with one completely missing and one not. 

5. And furthermore, there will be an issue when the group.by variable has more than two options, so i'd better deal with that now. 

6. Hmm, in order for this to work, I had to rewrite the vioplot function, since it had a weird thing where you passed it a number of vectors and it then created a list. Which doesnt' really work if you don't know how many vectors you have. 

7. Very annolyingly there seem to be some clipping of variable labels - descriptions. Which will be a pain for SH et al to have to deal with. But they were limited in the stata file to begin with - confirmed. So I guess I'll have to update them manually. 

8. So I have manually changed the variable descriptions for about 40 vasriables in the `02-data-clean.R` file.

9. OK, let's also try to add the household member stuff to the same file, to the women over 50. 

10. Hmm, looks like i stopped somewhere half way through changins sth in the members file, so that it's now missing the third section completley.. ffs. 

11. OK, i fixed the full members cut. 

12. Adding members to the women over 50, looks like there is at least one household where the respondent isn't in the B table. figure it out!

13. Christ, also looks like the female headed households are way larger than the others. 4.1 vs 3.4

# Friday 5.10. 2018

1. Clean up some details in the women over 50 cut in section B and C. There are clearly issues with the groups: in hh, not in hh, respondent. SO these household members dont' add up as one might wish..

OK, so do the following checks:

2. Is the number of unique housholds the same as the number of responents? The answer is no, there are actually two households where there was no 'respondent' logged in section B, these have been found and fixed.

3. By chance also found a family where the respondent was a widow, but there seemed to be a spouse in the household. i changed him to a son, since there was also a daughter in law, so was most likely. 

4. OK, so number of households and respondents are now the same. 

5. What are the numbers of respondents, other people in the same household, and other members not living there anymore. For total and for women over 50. OK, this is done, and the B-C section is celaned up in the over 50s women. I also added the group of all in household people. 

6. Added the "in household" group to the 03 cut of all the households.. 

7. OK, quick test: instead of provinces, which we have no reason to think will be interesting anyway, how about splitting the women into married and not married?

8. OK, did that, doesn't actually look particularly interesting.. 

9. OK, make all three versions of the women over over 50 and sent to SH.

!! Should I have a systematic system for dealing with errors like this that I fixed manually? That I guesstimate to be errors that I know how to fix? Or shoudl these cases be thrown out?

# Wednesday 10.10. 2018

1. OK, now the family typology, lets se what we have. 

2. Start report number 7 `r07-household-composition-typology.Rmd` with details on how it's done. 

3. Also added the file `X1-data-checking-additional.R` for the stuff from last time that lead to some people's relationship status to be changed. So this file is not on the pipeline, but explains some of the stuff in `02-data-clean`

4. OK so outline of report 7: 
* definitions of household types
* derivaiton of new variables
?! what about people in/out of the household?

5. OK, so definitions done. But need to figure out what to do about members migrated

6. New variables: 

* `hh.size` np
* `hh.size.net` - number of people in household - needed to change `n1` to an interval variable, because ohterwise it gets changed to a factor and can't be summed up
* `gen` - generation relative to respondent
* `n.gen` -  number of different generations in household

# Thursday 11.10. 2018

1. I can actually add summaries of these new variables to the extent they are interesting? Even better, do histograms of the full  survey data set and the women over 50s side by side. Then I can add the census data as well. 

2. OK, cleaned up, each variable has a summery data table and two histograms or barplots. 

3. Now try skipped generation houeholds using the funciton from the factsheet. 

4. But first add the net version of the number of generations in household

5. Now also add the skipped generations net of migrants. 


# Friday 12.10. 2018

1. Now let's try to put together the generation based typology. 

2. The migrants are an issue: what happens is that you can have a skipped generation household including the migrant, but in the household it is actually not. e.g. a granddaughter living away (e.g. household 122) . So we are interested in households that are skipped net of the migrants. 

3. OK, so they second typology seems to be simple enough, but it also looks like ther arean't any complex family types - but only because we only had one option for a non related household member, which is the servant. 

4. I could add single parent? Or widowed? How else can I describe the households, what other types of typologies are there? But sinle parent can be added to all of the categories in both classifications. 

5. OK, let's try to see who are the single parents - to the extent that it is even useful. So no spouse?

6. Also, in other news, an .Rdata file that has e.g. a memisc object in it cannot be loaded if the package isn't istalled. 

7. OK, so i've got a variable for single (not running any of this code, since i'm on the train anad didin't download the memics package before getting on the eurostar)

8. But these three should be enough. 

# Monday 15.10.2018

1. OK, ran some of the stuff i hadn't been able to do before witout the internet. 

2. There seems to be no number 13 i.e no composite households even though i thought there should have been one, need to manually check . 

3. Got it. it's because i keep forgetting to use as.numeric with these memisc items... when you do as.data.frame it pulls it out as a character vector..

4. OK, so looks like i have the famiuly typology wrking but it's pretty boring  really. I need to add at least the single partner one to make it more interesting. 

5. Aha, also the household typology summaries - i have to look at households, not at individuals! I basically have to change that in all the variable summaries except the relative generation one, that one is a individual level one, the remaining ones are household level. 

6. Also summaries: probably a reasonalble thing to do is to use frequencies in the table and proportions in the charts. Or maybe only proportions? If I make the N clear, then it's  easy for SH to calculate them if she wanted. 



<!--
  RANDOM COMMENTS, TO DO, KEEP FOR LATER..
TODO - a 'make file, that runs all the stuff in one go. 
TODO - missing values in table and chart
-->


<!--
rmarkdown::render("scripts/r01-data-analysis-journal.Rmd", output_format = "pdf_document", output_dir = "reports")
-->