---
title: "Vietnam FoF Survey Analysis - Journal"
author: "mz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
  number_sections: yes
toc: yes
toc_depth: 3
html_document: default
bibliography: "../misc/vn-lit.bib"
---
  
  ```{r "setup", include=FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require("knitr")
# opts_knit$set(root.dir = "/home/mz/Documents/Copy/Dropbox/analysis/Vietnam/VietnamSurvey")
opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
```


```{r "load data", include=FALSE}
# has to be in separate chunk from setup!
#load("data-old/working-copy.RData")
```

# Monday 23.10.2017 

Start checking new data.

Asked by GL to do a quick first trawl of the dataset. 

Move previous data into `data-old` folder start new journal - v.2


### Updated dir structure:

`*` indicate the folders and all their contents are hidden/non-public material. 
<!-- use tree /f /a > tree.txt to get output below -->
```
VietnamSurvey/
|   .gitignore
|   .Rhistory
|   VietnamSurvey.Rproj
|   
+---data/*
|   |   
|   \---data-raw/
|       +---DATA/
|       |   +---Excel/
|       |   |       Section_A-G.xls
|       |   |       Section_B.xls
|       |   |       Section_C.xls
|       |   |       Section_G3.xls
|       |   |       Section_H_K.xls
|       |   |       
|       |   \---Stata/
|       |           Section_A-G.dta
|       |           Section_B.dta
|       |           Section_C.dta
|       |           Section_G3.dta
|       |           Section_H_K.dta
|       |           
|       +---REPORT/
|       |       OIPA Farming Survey_IPPM Report_20170411.docx
|       |       
|       \---TOOLS/
|               OIPA_FoF Farming Quest_Eng_final_20161220.docx
|               OIPA_FoF Farming Quest_Vie_final_20161220.docx
|               
+---misc/
|       style.css
|       style.docx
|       vn-lit.bib
|       
+---old/*
|   +---data-old/*
|   |   |   full_data_v1_no_dup.dta
|   |   |   full_data_v1_no_dup_stata-12-11.dta
|   |   |   updated-copy.RData
|   |   |   working-copy.RData
|   |   |   
|   |   \---RawData/*
|   |           full_data_v1_no_dup.dta
|   |           OIPA_FoF Farming Quest_Eng_final_20161220.docx
|   |           OIPA_IPPM ToR for Survey in TB & VP Dec2016_final.pdf
|   |           
|   +---reports-old/*
|   |       r00-survey-variable-list-originals-only.pdf
|   |       r00-survey-variable-list.pdf
|   |       r01-data-analysis-journal-v01.pdf
|   |       r02-survey-issues.pdf
|   |       r03-first-cut.html
|   |       
|   \---scripts-old/*
|           00-my-functions.R 
|           00-scratchpad.R
|           01-data-import.R
|           02-new-variables.R
|           r00-survey-variable-list-originals-only.Rmd
|           r00-survey-variable-list.Rmd
|           r01-data-analysis-journal.pdf
|           r01-data-analysis-journal.Rmd
|           r02-survey-issues.docx
|           r02-survey-issues.Rmd
|           r03-first-cut.Rmd
|           
+---reports/*
\---scripts
        01-data-import.R
        r01-data-analysis-journal.Rmd
        style.docx
```


# Tuesday 24.10.2017 

* Clean up old stuff, now celar project
* Start import of data - `.dta` version
* Import Section_A-G.dta as `ds.1` 148 variables, 413 cases


# Thursday 26.10.2017 

* Import all 5 stata files, all 5 excel files and old stata file and compare number of cases


<!--
  RANDOM COMMENTS, TO DO, KEEP FOR LATER..
TODO - a 'make file, that runs all the stuff in one go. 
TODO - missing values in table and chart
-->


<!--
rmarkdown::render("scripts/r01-data-analysis-journal.Rmd", output_format = "pdf_document", output_dir = "reports")
-->