---
title: "Vietnam FoF Survey Analysis - Second dataset - First Trawl - Issues"
author: "mz"
html_document: default
output:
  pdf_document: 
    fig_caption: yes
  number_sections: yes
  html_document: default
  word_document:
    reference_docx: style.docx
bibliography: ../misc/vn-lit.bib
toc: yes
toc_depth: 3
---
  
```{r "setup", include=FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require("knitr")
library("captioner")
# opts_knit$set(root.dir = "/home/mz/Documents/Copy/Dropbox/analysis/Vietnam/VietnamSurvey")
opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
tbls <- captioner(prefix="Table")
```

```{r "load data", include=FALSE} 
# has to be in separate chunk from setup!
# load("data/working-copy.RData")
```

# Notes on first trawl 

This is a (slighlty) rambling write-up of things that came up during the first trawl of the dataset. 

## Import

We are provided with two versions of the data, one in `.dta` (stata) files and one in `.xls` (Excel) files. 

THESE ARE NOT THE SAME.

Importing the data is therefore an __opportinity__ to check for discrepancies. While I am at it, I check for how the new data compares with the old one as well.

### Section A-G
```{r captions, echo = FALSE, results='hide'}
tbls("T1","Row numbers for Sections A to G -- heads of household")
tbls("T2","Anomaly cases - heads of households")

```
* Importing section A-G from new files ( and comparing also to old)
* There are different numbers of cases, see table below.

`r tbls("T1")`
```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', fig_caption="Table 1"}

tabl <- "  
|  section      | Stata-new | Excel-new| [Stata-old] |
|---------------|:-------------:|:------:|:-----:|
| Section A-G   | 413 | 412 | [414] |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```



`r tbls("T1", display = "cite")`:  413-412 means there is an one person missing in the new Excel tables:

 * this is row 6 in `r tbls("T2", display = "cite")` below)
 
The difference wbetween 414 and 413 is actually more complicated: 

* Then there are two typos -(rows 1 and 3, and rows 2 and 4 below are presumably the same people)
* and finally there is row 5 in `r tbls("T2", display = "cite")`, a respondent that was in the original stata files, but not in the new ones. 

`r tbls("T2")`

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}

tab2 <- read.csv( "data/outputs/00.missing.cases.csv")

kable(tab2) # output the table in a format good for HTML/PDF/docx conversion


```



### Section B (hh members)
* Importing section B from new files 
* There are different numbers of cases, see table below.
* In old dataset B was in the same table as columns, and several rows actually have the wron hh

```{r table3, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', tab.cap="Table 1"}
tabl <- "  
|  section      | Stata-new | Excel-new| [Stata-old] |
|---------------|:-------------:|:------:|:-----:|
| Section B   | 1483 | 1482 | [1485] |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

There are two types of anomalies:
* one person only in the new stata file, but not in the new Excel file (row 3 below) 
* two family members that were in the original data, but not in the new one (row 1 and 2 below) -- incidentally, these belong to the same hh as the now missing head of in row 5 above. 

```{r table4, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tab4 <- read.csv( "data/outputs/01.missing.cases.2.csv")

kable(tab4) # output the table in a format good for HTML/PDF/docx conversion
```


### Section C (hh members living away)
* Importing section C from new files 
* Number of cases looks OK, matched for main key variables as well.

```{r table5, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', tab.cap="Table 1"}
tabl <- "  
|  section      | Stata-new | Excel-new| [Stata-old] |
|---------------|:-------------:|:------:|:-----:|
| Section C   | 113 | 113 | [113] |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```


## Random niggles

* Seriously, why are there no IDs, this is making my life incredibly difficult... 


<!--
rmarkdown::render("scripts/r02-survey-issues.Rmd", output_format = "pdf_document", output_dir = "reports")
-->