---
title: "Vietnam FoF Survey Analysis---Second dataset---Issues"
author: "mz---30.10.17"
html_document: default
output:
  word_document:
    reference_docx: style.docx
  pdf_document:
    number_sections: yes
  html_document: default
bibliography: ../misc/vn-lit.bib
toc: yes
toc_depth: 3
---
  
```{r "setup", include=FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require("knitr")
library("captioner")
# opts_knit$set(root.dir = "/home/mz/Documents/Copy/Dropbox/analysis/Vietnam/VietnamSurvey")
opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
tbls <- captioner(prefix="Table")
```

```{r "load data", include=FALSE} 
# has to be in separate chunk from setup!
# load("data/working-copy.RData")
```

# Overview

## Sampling of districts

The report on the survey that accompanies this dataset has a description of the district and commune selection. Their "Section 1.2: choice of surveyed locations" describes the methodology and Appendix 1. and 2. the data for selecting the districts. I didn't go into detail, but there are errors in how the tables were calculated, e.g. all the totals and averages in the last 4 columns of the Table A1-1 are wrong. Presumably that measn the districts were based on these wrong statistics. 

## Sampling of households
It is to be concluded from the report that respondents were required to be doing __only__ agriculural jobs. I'm not sure if I got this right, but it seems like respondents who were doing any casual or part time non-agricultural work were excluded? [This is the reason tehre are only 22 people unde 50 in the sample]

There is still no explanation in the survey report for the dramatic gender ratio in the Vinh Phuc province (32 Males to 178 Females).

## Questionnaires

Comared to the previous version the stata files are now correctly annotated and labeled. But reference to English questionnaires shows the labels are not the same - i.e. the Vientamese categories were changed and the English version of the questionnaire not updated (e.g. question c4 or g33). 

## Data files

See next section for details on this, but essentially the 10 data files provided (5 stata and 5 Excel) are not perfectly compatible. 

1. There is a household missing in two of the Excel files
2. (There is also household in the original data, that is missing in the new data.)
3. There is a household member missing in the Excel file
4. (The hh members of the hh from point 2 are also missing in the new data.)
5. There are two households who's members are missing from the new files completely
6. There are 3 miscoded 'relationship to head' members in Section B.
7. There was at least one hh member in the Section C files that had been wrongly entered and I had to delete. 


## Other

Most of the other issues in the previous dataset had to do with no coding, or no labels, and these seem to have mostly been fixed in this version - but I'll only be able to confirm when I do the first trawl through. 





# Notes on data Import  

This is a (slighlty) rambling write-up of things that came up during the first trawl of the dataset. 

We are provided with two versions of the data, one in `.dta` (stata) files and one in `.xls` (Excel) files. 

__THESE ARE NOT THE SAME.__ Importing the data is therefore an opportinity to check for discrepancies. While I am at it, I check for how the new data compares with the old one as well.

### Section A-G (hh heads)
```{r captions, echo = FALSE, results='hide'}
tbls("T1","Row numbers for Sections A to G--heads of household")
tbls("T2","Anomaly cases Sections A to G--heads of households")
tbls("T3","Row numbers for Section B--household members in hh")
tbls("T4","Anomaly cases Section B--household members in hh")
tbls("T5","Row numbers for Section C--household members living away")
tbls("T6","Anomaly cases Section C--household members living away")
tbls("T7","Row numbers for Section C--plots of land growing rice")
tbls("T8","Row numbers for Sections G to H--heads of households")
tbls("T9","Anomaly cases Sections G to H--heads of households")
tbls("T10","Consolidated datasets after clean import")
tbls("T11","Anomaly cases--have Sections A-G, but wihtout section B")
tbls("T12","Anomaly cases--wrong relationship in section B")
```
* Importing section A-G from new files ( and comparing also to old)
* There are different numbers of cases, see table below.

`r tbls("T1")`
```{r table1, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', fig_caption="Table 1"}

tabl <- "  
|  section      | Stata-new | Excel-new| [Stata-old] |
|---------------|:-------------:|:------:|:-----:|
| Section A-G   | 413 | 412 | [414] |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```



In the above `r tbls("T1", display = "cite")`:  the difference 413-412 means there is an one person missing in the new Excel tables:

 * this is row 6 in `r tbls("T2", display = "cite")` below)
 
The difference wbetween 414 and 413 is actually more complicated: 

* Then there are two typos -(rows 1 and 3, and rows 2 and 4 below are presumably the same people)
* and finally there is row 5 in `r tbls("T2", display = "cite")`, a respondent that was in the original stata files, but not in the new ones. 

`r tbls("T2")`

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}

tab2 <- read.csv( "data/outputs/00.missing.cases.csv")

kable(tab2) # output the table in a format good for HTML/PDF/docx conversion


```



### Section B (hh members)
* Importing section B from new files 
* There are different numbers of cases, see table below.
* In old dataset B was in the same table as columns, and several rows actually have the wron hh

`r tbls("T3")`

```{r table3, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', tab.cap="Table 1"}
tabl <- "  
|  section      | Stata-new | Excel-new| [Stata-old] |
|---------------|:-------------:|:------:|:-----:|
| Section B   | 1483 | 1482 | [1485] |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

There are two types of anomalies:

* one person only in the new stata file, but not in the new Excel file (row 3 below) 
* two family members that were in the original data, but not in the new one (row 1 and 2 below) -- incidentally, these belong to the same hh as the now missing head of in row 5 above. 

`r tbls("T4")`

```{r table4, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tab4 <- read.csv( "data/outputs/01.missing.cases.2.csv")

kable(tab4) # output the table in a format good for HTML/PDF/docx conversion
```

Aah, but there is another problem as well. Because hh. members also inlcudes respondents, I can do another check and compare hh members in this file who are coded as the respondents, with the cases in the first section. (only noticed this later, but had to go back and fix here in the import to keep it tidy)

So there are two issues here.

1. There are two households that are completely missing from Section B:

`r tbls("T11")`
```{r table11, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tab4 <- read.csv( "data/outputs/04.missing.cases.5.csv")

kable(tab4) # output the table in a format good for HTML/PDF/docx conversion
```

And it is clear even from this that one of them (the one in row 2) had at least one other household member __because their name is right there__. Anyway, having another hh member is not a prerequisite for Seciton B, so both of these should be there.

2. There are three household where Section B has two people listed as respondents in each of them: 
`r tbls("T12")`
```{r table12, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tab4 <- read.csv( "data/outputs/05.missing.cases.6.csv")

kable(tab4) # output the table in a format good for HTML/PDF/docx conversion
```

I guess I can assume the second in each of these is not actually the respondent. But who are they? The one in row 2 could be  the spouse reasonably? The one in row 4 could be tge daughter? And thw last one? Presumably not same sex partner?


OK, so all the ones in `r tbls("T12", display = "cite")` I have to make their relationship "missing". 

And the two households in `r tbls("T11", display = "cite")`, I'll leave them in, but make sure when household stuff is derived they will have missing values there, so can't get included in the analysis. So there are only 411 respondents in the hh members file, not 413 as we would expect. 


### Section C (hh members living away)
* Importing section C from new files 
* Number of cases looks OK, matched for main key variables as well.

`r tbls("T5")`

```{r table5, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', tab.cap="Table 1"}
tabl <- "  
|  section      | Stata-new | Excel-new| [Stata-old] |
|---------------|:-------------:|:------:|:-----:|
| Section C   | 113 | 113 | [113] |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

* So this looks good, but comparing the new stata and Excel files in more detail shows that there is at least one error: A missing value `c4` in the stata file, that is in the Excel one however. 
* (this is not the year of birth, 1989 is also wrong, this should be the answer to the question 'where is this family member residing')
* Furthermore this person is both 'male' and a 'daughter', which is clearly an issue. [checked gender cosnistency for the rest of Section C and this was teh only error]. 
* This case __is removed from the dataset__. (number of cases is now 112)

`r tbls("T6")`
```{r table6, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tab6 <- read.csv( "data/outputs/02.missing.cases.3.csv")

kable(tab6) # output the table in a format good for HTML/PDF/docx conversion
```


### Section G3 (rice plots)
* Importing section G3 from new files 
* Number of cases looks OK, matched for main key variables as well.

`r tbls("T7")`

```{r table7, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', tab.cap="Table 1"}
tabl <- "  
|  section      | Stata-new | Excel-new| [Stata-old] |
|---------------|:-------------:|:------:|:-----:|
| Section G3   | 1396 | 1396 | [1396] |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

* Double checking shows __both new files are in fact identical__. 
* Comparison to old file showed there were a few missing values in the old one that seem to have been replaced now, nothing worth mentioning I guess though. 


### Section G-H (heads of households again)
* Importing section G-H from new files 
* Number of cases again missing one in the Excel files. and one extra one from the old files

`r tbls("T8")`

```{r table8, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', tab.cap="Table 1"}
tabl <- "  
|  section      | Stata-new | Excel-new| [Stata-old] |
|---------------|:-------------:|:------:|:-----:|
| Section G-H   | 413 | 412 | [414] |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

* The respondent missing from the new Excel files (row 6 in `r tbls("T9", display = "cite")` below) is __not the same one as was missing from the first section__ (row 6 in `r tbls("T2", display = "cite")` above)!!
* the differences with the old data are the same however: two typos (row 1=3 and row 2=4) and the same person in row 5 is only in the original data (and their family) but not in the new one. 

`r tbls("T9")`

```{r table9, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}

tab9 <- read.csv( "data/outputs/03.missing.cases.4.csv")

kable(tab9) # output the table in a format good for HTML/PDF/docx conversion

```

## Clean import

From now on everything is based on the new stata files:

* with the removal of the case described in  `r tbls("T6", display = "cite")` above
* merge together section S-G and G-H files as both have heads of households as basic units. 
* merge together section B and C files as both have household members as basic units. 
* add unique IDs to households and members. 

The numbers of cases and variables are described in the `r tbls("T10", display = "cite")` 

`r tbls("T10")`
```{r table10, echo=FALSE, message=FALSE, warnings=FALSE, results='asis', tab.cap="Table 1"}
tabl <- "  
|  table name | section names     | case type   | number of cases  | number of variables |
|---------|---------|-------------|------|-----|
| ds.hohh  | Section A,D,E, G, H, I, K  | head of household | 413 | 262 |
| ds.mmbr  |  Section B and C | hh members in hh | 1483 + 112 = 1595 | 11 |
| ds.plot |  Section G3 | rice plots | 1396 | 10 |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```


## Random niggles

* Seriously, why are there no IDs, this is making my life incredibly difficult... 
* also, if they had IDs then most of the errors I found could never have occured... 

<!--
rmarkdown::render("scripts/r02-survey-issues.Rmd", output_format = "pdf_document", output_dir = "reports")
-->