---
title: "Vietnam FoF Survey - First Cut"
tables: yes
output:
  html_document:
    css: ../misc/style.css
    toc: yes
---

```{r "setup", include=FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require("knitr")
require("memisc")
opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
```

  
```{r intro, echo = FALSE, warning = FALSE, message = FALSE}
source("scripts/00-my-functions.R")
load("data/updated-copy.RData")
```  

* *All  frequency tables are in column percentages*
* *Widths of barplots are proportional to size of group*


# A. Personal Information

`r var <- ds$a1`
## a1-`r description(I(var))` 
[N = `r sum(!is.na(var))`] 

```{r results='asis', echo=FALSE, fig.height=5}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$a2`
## a2-`r description(I(var))` 
[N = `r sum(!is.na(var))`] 


```{r results='asis', echo=FALSE, fig.height=5}
FunTop(var)
FunIntervalTable(var)
FunIntervalBoxplot(var)
```

`r var <- ds$n2`
## n2-`r description(I(var))` 
[N = `r sum(!is.na(var))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunIntervalTable(var)
FunIntervalBoxplot(var)
```

`r var <- ds$a3`
## a3-`r description(I(var))` 
[N = `r sum(!is.na(var))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$a4`
## a4-`r description(I(var))` 
[N = `r sum(!is.na(var))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$a5`
## a5-`r description(I(var))` 
[N = `r sum(!is.na(var))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$a6`
## a6-`r description(I(var))` 
[N = `r sum(!is.na(var))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```



# B. Information about those who are currently living in the same household


# C. Information about those who are currently NOT living in the same household


# D. Information about rice farming and family responsibilities 

`r var <- ds$d1`
## d1-`r description(I(var))` 
[N = `r sum(!is.na(var))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

<!--
rmarkdown::render("scripts/r03-first-cut.Rmd", output_format = "html_document", output_dir = "reports")
-->