---
title: "Vietnam FoF Survey---First Cut--Household Members"
tables: yes
output:
  pdf_document: default
  html_document:
    css: ../misc/style.css
  word_document: default
toc: yes
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../reports") })
---
  
```{r "setup", include=FALSE, message = FALSE, warning = FALSE, echo= FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require(knitr)
require(memisc)

opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
```


```{r intro, echo = FALSE, warning = FALSE, message = FALSE}
source("scripts/00-functions.R")
load("data/outputs/clean.Rdata")
```  

* *All  frequency tables are in column percentages*
 * *Widths of barplots are proportional to size of group*
  
  
# Household members - all 1595 of them

This first cut uses all 1595 household members in the dataset, this is both Section B, those living in the household (inlcuidng respondents) and Section C (not living in Household)
  
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c(6, 8:11)){
  FunTop(i , 
            tab = ds.mmbr,
                   group.by = "province")
}
```

# Household members living in Household 

This second one  cut uses all 1483 household members in the dataset living in the household 
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c(6, 8:11)){
  FunTop(i , 
            tab = subset(ds.mmbr, n1 == 1),
                   group.by = "province")
}
```

# Household members living in Household, but without respondents themselves. 

This second one  cut uses all 1070 household members in the dataset, except respondents, living in the household 
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c(6, 8:11)){
  FunTop(i , 
            tab = subset(ds.mmbr, n1 == 1 & n4 != 1 ),
                   group.by = "province")
}
```


# Household members not living in Household

This third one  cut uses  112 household members in the dataset who are not living in the hosuehold ( Section C -not living in Household)
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c(6, 8:11)){
  FunTop(i , 
            tab = subset(ds.mmbr, n1 != 1 ),
                   group.by = "province")
}
```

