---
title: "Vietnam FoF Survey---First Cut (second try)"
tables: yes
output:
  word_document: default
  pdf_document: default
  html_document:
    css: ../misc/style.css
    toc: yes
toc: yes
---
  
```{r "setup", include=FALSE, message = FALSE, warning = FALSE, echo= FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require(knitr)
require(memisc)

opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
```


```{r intro, echo = FALSE, warning = FALSE, message = FALSE}
source("scripts/00-functions.R")
load("data/outputs/clean.Rdata")
```  

* *All  frequency tables are in column percentages*
* *Widths of barplots are proportional to size of group*
  
  
# Section A. Personal information


```{r results='asis', echo=FALSE, fig.height=5}
for (i in 10:15){
FunTop(i)
}
```

  
#  Section D. Information about rice farming and family responsibilities 

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 16:23){
FunTop(i)
}
```

# Section E. Health situation and capability to follow farming tasks 
```{r results='asis', echo=FALSE, fig.height=5}
for (i in 24:42){
FunTop(i)
}
```



# Module 2. FARMING – GENERAL DESCRIPTION -- Section G

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 43:149){
FunTop(i)
}
```

# Module 3. FARMING – BEHAVIOUR, KNOWLEDGE/CHOICES, OPINIONS -- Section H

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 149:208){
FunTop(i)
}
```

# Module 4-- Section I – Rice Varieties

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 209:236){
FunTop(i)
}
```

# Module 4-- Section K – Pesticide Use

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 237:262){
FunTop(i)
}
```
<!--
  rmarkdown::render("scripts/r03-first-cut.Rmd", output_format = "html_document", output_dir = "reports")
-->