---
title: "Vietnam FoF Survey - First Cut"
tables: yes
output:
  html_document:
    css: ../misc/style.css
    toc: yes
---

```{r "setup", include=FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require("knitr")
require("memisc")
opts_knit$set(root.dir = "/home/mz/Documents/Copy/Dropbox/analysis/Vietnam/VietnamSurvey")
```

  
```{r intro, echo = FALSE, warning = FALSE, message = FALSE}
source("scripts/00-my-functions.R")
load("data/updated-copy.RData")
```  

* *All  frequency tables are in column percentages*
* *Widths of barplots are proportional to size of group*


# A. Personal Information

`r var <- ds$a1`
## a1 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=5}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$a2`
## a2 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 


```{r results='asis', echo=FALSE, fig.height=5}
FunTop(var)
FunIntervalTable(var)
FunIntervalBoxplot(var)
```

`r var <- ds$n2`
## n2 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunIntervalTable(var)
FunIntervalBoxplot(var)
```

`r var <- ds$a3`
## a3 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$a4`
## a4 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$a5`
## a5 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$a6`
## a6 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```



# B. Information about those who are currently living in the same household


# C. Information about those who are currently NOT living in the same household


# D. Information about rice farming and family responsibilities 

`r var <- ds$d1`
## d1 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$d21`
## d21 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$d22`
## d22 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$d23`
## d23 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$d31`
## d31  -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$d32`
## d32 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$d33`
## d33 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$d34`
## d34 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```



# E. Health situation and capability to follow farming tasks 

`r var <- ds$e1`
## e1 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e211`
## e211 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e221`
## e221 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e231`
## e231 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```




`r var <- ds$e212`
## e212 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e222`
## e222 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e232`
## e232 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```



`r var <- ds$e213`
## e213 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e223`
## e223 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e233`
## e233 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$e214`
## e214 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e224`
## e224 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e234`
## e234 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$e215`
## e215 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e225`
## e225 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e235`
## e235 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```



`r var <- ds$e216`
## e216 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e226`
## e226 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

`r var <- ds$e236`
## e236 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

# Module 2:  Farming – GENERAL DESCRIPTION

`r var <- ds$g1`
## g1 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=5}
FunTop(var)
FunIntervalTable(var)
FunIntervalBoxplot(var)
```


`r var <- ds$g2`
## g2 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

# Module 3 : Farming – behaviour, knowledge/choices, opinions

`r var <- ds$h1a`
## h1a -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$h1b`
## h1b -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


`r var <- ds$h1c`
## h1c -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```

# Module 4: Rice Varieties and Preventative Pesticide Spraying

`r var <- ds$i1`
## i1 -`r description(I(var))` 
[N = `r sum(!is.na(as.numeric(var)))`] 

```{r results='asis', echo=FALSE, fig.height=4}
FunTop(var)
FunNominalTable(var)
FunNominalBarplot(var)
```


<!--
rmarkdown::render("scripts/r03-first-cut.Rmd", output_format = "html_document", output_dir = "reports")
-->