---
title: "Vietnam FoF Survey---First Cut--Household Members"
tables: yes
output:
  html_document:
    css: ../misc/style.css
  pdf_document: default
  word_document: default
toc: yes
---
  
```{r "setup", include=FALSE, message = FALSE, warning = FALSE, echo= FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require(knitr)
require(memisc)

opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
```


```{r intro, echo = FALSE, warning = FALSE, message = FALSE}
source("scripts/00-functions.R")
load("data/outputs/clean.Rdata")
```  

* *All  frequency tables are in column percentages*
  * *Widths of barplots are proportional to size of group*
  
  
# Household members - all 1595 of them

This first cut uses all 1595 household members in the dataset, this is both Section B, those living in the household (inlcuidng respondents) and Section C (not living in Household)
  
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c(6, 8:11)){
  FunTopM(i)
}
```

# Household members living in Household, but without respondents themselves. 

This second one  cut uses all 1072 household members in the dataset, except respondents, this is both Section B, those living in the household and Section C (not living in Household)
  
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c( 8:11)){
  FunTopM.no.resp(i)
}
```

# Household members not living in Household

This third one  cut uses  112 household members in the dataset who are not living in the hosuehold ( Section C -not living in Household)
  
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c( 8:11)){
  FunTopM.C(i)
}
```
