---
title: "Vietnam FoF Survey---Women over 50"
tables: yes
output:
  pdf_document: default
  word_document: default
  html_document:
    css: ../misc/style.css
    toc: yes
toc: yes
---
  
```{r "setup", include=FALSE, message = FALSE, warning = FALSE, echo= FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require(knitr)
require(memisc)

opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
```


```{r intro, echo = FALSE, warning = FALSE, message = FALSE}
source("scripts/00-functions.R")
load("data/outputs/clean.Rdata")

#  select only women over the age of 50 
ds.hohh[ds.hohh$a1 == "Female"& ds.hohh$a2 <= 1966, ] -> ds.hohh.w.50
ds.mmbr[ds.mmbr$hh.id %in% ds.hohh.w.50$hh.id , ] -> ds.mmbr.w.50

```  

* *All  frequency tables are in column percentages*
* *Widths of barplots are proportional to size of group*
  
  
# Section A. Personal information
  
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in 10:15){
  FunTop(i, tab = ds.hohh.w.50)
}
```

# Sections B and C on household members
  
## Household members - all 1595 of them

This first cut uses all 1033 household members in households where the respondents were women over 50. 
  
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c(6, 8:11)){
  FunTop(i , 
            tab = ds.mmbr.w.50,
                   group.by = "province")
}
```

## Household members living in Household, but without respondents themselves. 

This second one  cut uses all 1072 household members in the dataset, except respondents, living in the household 
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c(6, 8:11)){
  FunTop(i , 
            tab = subset(ds.mmbr.w.50, n1 == 1 & n4 != 1 ),
                   group.by = "province")
}
```


## Household members not living in Household

This third one  cut uses  112 household members in the dataset who are not living in the hosuehold ( Section C -not living in Household)
  
```{r results='asis', echo=FALSE, fig.height=5}
for (i in c(6, 8:11)){
  FunTop(i , 
            tab = subset(ds.mmbr.w.50, n1 != 1 ),
                   group.by = "province")
}
```


#  Section D. Information about rice farming and family responsibilities

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 16:23){
  FunTop(i, tab = ds.hohh.w.50)
}
```

# Section E. Health situation and capability to follow farming tasks
```{r results='asis', echo=FALSE, fig.height=5}
for (i in 24:42){
  FunTop(i, tab = ds.hohh.w.50)
}
```

# Module 2. FARMING – GENERAL DESCRIPTION -- Section G

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 43:148){
  FunTop(i, tab = ds.hohh.w.50)
}
```

# Module 3. FARMING – BEHAVIOUR, KNOWLEDGE/CHOICES, OPINIONS -- Section H

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 149:208){
  FunTop(i, tab = ds.hohh.w.50)
}
```

# Module 4-- Section I – Rice Varieties

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 209:236){
  FunTop(i,tab = ds.hohh.w.50)
}
```

# Module 4-- Section K – Pesticide Use

```{r results='asis', echo=FALSE, fig.height=5}
for (i in 237:262){
  FunTop(i,tab = ds.hohh.w.50)
}
```
<!-- <!-- -->
<!--   rmarkdown::render("scripts/r03-first-cut.Rmd", output_format = "html_document", output_dir = "reports") -->
<!-- --> -->