---
title: "Vietnam FoF Survey---Household Composition Typology"
author: maja
date: "10.10.2018"
tables: yes
output:
  pdf_document: default
  word_document: default
toc: yes
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../reports") })
bibliography: ../reports/bib.bib
---
  
```{r setup, include=FALSE, message = FALSE, warning = FALSE, echo= FALSE}
## this is to set up the main folder as the root
## although this doesnot work for the YAML designations e.g. bibliography, css files etc..:(
require(knitr)
require(dplyr)
require(memisc)

opts_knit$set(root.dir = "C:/Users/sfos0247/Dropbox/analysis/Vietnam/VietnamSurvey")
```


```{r intro, echo = FALSE, warning = FALSE, message = FALSE}
load("data/outputs/clean.Rdata")

#  select only women over the age of 50 
ds.hohh[ds.hohh$a1 == "Female"& ds.hohh$a2 <= 1966, ] -> ds.hohh.w.50
ds.mmbr[ds.mmbr$hh.id %in% ds.hohh.w.50$hh.id , ] -> ds.mmbr.w.50

```  
# Intro

This material is prepared as discussed in the 3.10. meeting with SH, GWL and KH as a potential basis for SH's paper on older women based on the Vientam survey data. 

I set out the typologies and the data first. 

# Household typologies

I start out with two typologies: 

1. *Family-based*: The UN recommended household classification based on family nuclei and the relationship between the nuclei and other members in the hosuehold (see @un2017principles)
2. *Generation-based*: An ad-hoc classification I used in the household living arrangemnts factsheet (@2016mz) and is based on the generational structure of the household. 

These two typologies could of course be modified, depending on what you want to focus on. 

## Family-based classification

At the top level this classificaiton has four main types: 

1. *One person household*—A single person living alone. This is defined the same in both typologies presented here.
2. *Nuclear household*—a couple with or without children, or a single parent.
3. *Extended household*—members beyond the family nucleus are related by blood or marriage.
4. *Composite household*-other persons are present who are not related to the head.

## Generation-based classification

At the top level this classificaiton has five main types: 

1. *One person household*—A single person living alone. This is defined the same in both typologies presented here.
2. *One generation household*—at least one more person of the same age group as the head Usually a spouse, but can also be sibling etc.
3. *Two generation household*—at least one more person one generation younger/older than the head. Usually child(ren), can also be parent etc. 
4. *Three or more generation household*—at least two more persons of different generations than the head (but without skipping generations).
5. *Skipped generation household*—at least one generation missing. Usually head with grandchildren but without children.


# Data availability and preparation

## Available data

The main variable of interest, `n4 - Relationship with the respondent`, has the following values and distribution in the population of households members living in households headed[^1] by women over the age of 50 (N = `r nrow(ds.mmbr.w.50)`):

```{r prepare, echo = FALSE, warning = FALSE, message = FALSE}
codebook(ds.mmbr.w.50$n4)
```

So a random household e.g. looks like this:
```{r echo = FALSE}
ds.mmbr.w.50$n4[ds.mmbr.w.50$hh.id == 2,]
```

## Data Preparation

The following variables are derived in order to facilitate the identificiation of household types:

1. `hh.size` - Household size.
2. `hh.size.net` - Household size net of migrants
3. `gen` - generation code = relative to the respondent, who is at 0, children are 1, parents are -1 etc. 
4. `n.gen` - Number of different generations in household

[^1]: It is not precisely clear to what extent these households can be said to be *headed* by these women, rather they were selected to be the respondents in this survey as they had the most knowledge or were most involved in the decision-making when it came to farming. 
# References


